---
title: 'STAT 443: Lab10'
author: 'Lai Wei (#31739014)'
date: "28 March, 2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#if you do not have the package, type install.packages("name_of_the_package")
library(knitr)
library(tseries)
```

### Question 1
(a)
```{r,echo=TRUE}
#spectural density function
plot(c(0,pi),c(4/pi,4/pi),type="l",xlab="w",ylab="I(w_p)")
```
(b)
```{r,echo=TRUE}
z<-arima.sim(n=100,list(order=c(0,0,0)),sd=sqrt(4))
spec.pgram(z,log="no")
#comment:
#the periodogram seems to be centered around true value 4. But the plot here has a lot of variations.
```
(c)
```{r,echo=TRUE}
z2<-arima.sim(n=1000,list(order=c(0,0,0)),sd=sqrt(4))
spec.pgram(z2,log="no")
#comment:
#the periodogram seems to be centered around true value 4.and this plot still has a lot of variantion.the larger sample size seem not helping in reducing the variance. the plot with larger sample size looks like more density
```

(d)
```{r,echo=TRUE}
# repeat (b) and (c) several times,how the periodogram from R behaves as an estimator of the spectral density function based on what you have observed.

# Periodogram is an asmptotically unbiased estimator for spectrum, but it is not consistent.
```

### Question 2
(a)
```{r,echo=TRUE}
beta<- -0.9
fw<-function(w){
  return((1+beta^2)*4*1/pi*(1+2*beta*cos(w)/(1+beta^2)))
}

w_value<-seq(0,pi,length.out = 100)
plot(w_value,fw(w_value),type="l")

```
(b)
```{r,echo=TRUE}
ma<-arima.sim(n=100,list(ma=c(-0.9)),sd=2)
spec.pgram(ma,log="no")

#the periodogram captures the overall shape of specturm,that is,small on low frequency, large on high frequency.
```
(c)
```{r,echo=TRUE}
ma2<-arima.sim(n=100,list(ma=c(-0.9)),sd=2)
spec.pgram(ma2,log="no")
#the periodogram captures the overall shape of spectrum,that is,small on low frequency, large on high frequency. with larger sample szie, the variation goes smaller.
```
(d)
repeat (b) and (c) several times,how the periodogram from R behaves as an estimator of the spectral density function based on what you have observed.

Periodogram is an asmptotically unbiased estimator for spectrum, but it is not consistent.


### Question 3
(a)
```{r,echo=TRUE}
#plot the sepctral for X_t
fw<-function(w){
  return(4/pi/(1-1.6*cos(w)+0.8^2))
}

w_value<-seq(0,pi,length.out = 100)
plot(w_value,fw(w_value),type="l")

```
(b)
```{r,echo=TRUE}
ar<-arima.sim(n=100,list(ar=c(0.8)),sd=2)
spec.pgram(ar,log="no")
#the periodogram captures the overall shape of frequency waves: large on low frequency, small on high frequency.
```

(c)
```{r,echo=TRUE}
ar2<-arima.sim(n=1000,list(ar=c(0.8)),sd=2)
spec.pgram(ar2,log="no")
#the periodogram captures the overall shape of frequency waves: large on low frequency, small on high frequency, with larger sample size, the variation goes smaller.
```
(d)
repeat (b) and (c) several times,how the periodogram from R behaves as an estimator of the spectral density function based on what you have observed.

Periodogram is an asmptotically unbiased estimator for spectrum, but it is not consistent.

